---
title: "Econ 258: Looping Things!"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include = FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)

library(reshape2)
library(ggplot2)

```

```{r setup, include = FALSE}
```


## Loop practice.  

*Here are some practice loop exercise. No solution suggestion for this week. But those who finished could post their solution on Yellowdig for points. Also can see if people have different ways to code this.*


Use a "while" loop command to add print multiples of 3s until the number 30 then stop. 
```{exercise q1, exercise = TRUE}
i <- 3 
while(i<31){
  print(i)
  i <- i+3
}
```

Can you create a loop similar to the lesson code that changes 6,7,8,9,10 into 0s? See if you can replicate it without looking at the code or find a better way to do this. 

```{exercise q2, exercise = TRUE}
vector <- c(1,2,3,4,5,6,7,8,9,10)
for(k in 1:10){
  if(vector[k]>5){
    vector[k] <- 0
  }
}
vector
```

Use a for loop command to loop through number 1,3,5,7, and 10. With each loop, have an output printing the number + 3. Hint: you might want to create a vector first for values you are looping under. 

```{exercise q3, exercise = TRUE}
v <- c(1,3,5,7,10)
for(k in 1:5){
  print(v[k] <- v[k] + 3)
}
```

